|

### 2021-09-09 article/article.Rmd
remove binom tests, edits to table 2 and text

---
title:  |
        | The Effect of Legislature Size on Public Spending:
        | A Meta-Analysis
date: \today
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we conduct the first meta-analysis that assesses the generality of the \"law of $1/n$\". Based on a sample of 30 articles, we find no robust evidence for the effect of legislature size on government budgets. Yet the aggregate results show significant heterogeneity. We find moderate support for the \"law of $1/n$\" in unicameral legislatures and in the upper house, but panel/fixed-effects models and regression discontinuity designs reduce public spending estimates. Our results also indicate that proportional representation systems are no more likely to overspend than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

@@

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We select `r length(unique(dat$id))` articles that
use quantitative methods to evaluate the impact of legislature size over
government spending across several dimensions. Our study sample mirrors the
diversity of the literature. Out of the `r dim(dat)[1]` coefficients
included in our main analysis, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Given the volume and the disparity of
the studies, we employ meta-analysis to summarise the results. Meta-analysis
provides a rigorous approach to combine heterogeneous outcomes into a single
estimation, and it allows scholars to gain valuable insights from the
aggregated data [@cooper2019handbook; @hedges1985statistical]. Meta-analysis
can also identify potential sources of study variability, enabling researchers
to assess threats to external validity and direct future efforts into more
promising areas of academic inquiry [@doucouliagos2008democracy]. Research
synthesis methods have been successfully applied in medicine and psychology
since the 1970s [@glass2015meta], and our work contributes to the burgeoning
literature that uses meta-analytic methods to understand challenging questions
in political science [@costa2017responsive; @doucouliagos2008democracy;
@green2013field; @lau2007effects; @schwarz2020supporting].

We run binomial tests and meta-regressions to further evaluate the relationship
between legislature size and government expenditures. We use binomial tests to
assess whether the proportions of positive and negative coefficients in our
sample are statistically different from each other. In the meta-regressions, we
measure the effect of five moderators that capture different sources of
heterogeneity in the literature. We also construct a series of funnel plots to
test for publication bias in existing research on the "law of $1/n$"
[@easterbrook1991publication; @gerber2001testing].

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
aux$`Independent Variables` <- recode(aux$`Independent Variables`,
                                      `N` = "Lower Chamber Size",
                                      `K` = "Upper Chamber Size",
                                      `logN` = "Log of Lower Chamber Size")
aux$`Electoral system` <- recode(aux$`Electoral system`,
                                 `Non-Maj` = "Non-Majoritarian",
                                 `Maj` = "Majoritarian")
aux <- select(aux, usemeta2, `Independent Variables`, Year, `Published work`, `Estimation method`, `Institutional Design`, `Electoral system`)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive statistics of moderators",
          format  = "latex")
```
\normalsize

@@

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency and improving
the accuracy of the results. More information about the multilevel models can
be found in Section H.1 of the Supplementary Material.

@@

The "law of $1/n$" states that more legislators increase government
expenditure. In this paper, we employ three methods to test the empirical
validity of that relationship. First, we run binomial z-tests to assess the
frequency of positive and negative coefficients in our sample. Then, we fit
nine multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
`dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
Lastly, we run four sets of meta-regressions to measure the effects of a group
of moderators on the effect sizes of our study sample. To recapitulate, our
independent variables of interest are lower chamber size, the natural logarithm
of lower chamber size, and upper chamber size. The dependent variables are
public expenditure per capita, the natural logarithm of public expenditure per
capita, and government expenditure as a percentage of GDP. Since the outcomes
have different scales, we treat them separately in our models.

@@

## Binomial Z-Tests
\label{sub:binomial}

The binomial z-test evaluates whether the majority of the coefficients of our
independent variables are positive or negative[^binomial]. If increasing the
number of legislators leads to higher public expending, we should expect most
coefficients to be positive. Conversely, if the "reverse law of $1/n$" is true,
our results should indicate that $p < 0.5$, that is, the proportion of positive
coefficients is lower than 0.5. The null hypothesis here states that the sign
of the coefficient is equally likely to be positive or negative.

[^binomial]: Since coefficients are either positive or negative, each of them
can be considered a Bernoulli trial. Thus, the aggregate results for all papers
follow a Binomial distribution where parameters $n$ equals the number of papers
and $p$ is the chance of a positive coefficient. The "law of $1/n$" can be
reformulated as the chance of $p > 0.5$, which facilitates the testing of the
theory.

We start with lower house size. Our results indicate that there is no
correlation between the number of legislators in the lower house and public
expenditure (successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`], $p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for the natural logarithm of lower
chamber size also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house, which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`).

@@

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the nine variable combinations, we found only seven the article
pool. Our sample does not contain any papers that analyse the relationships
between log lower chamber size and public expenditure per capita, or between
upper chamber size and the logarithm of public expenditure per capita.

@@

\begin{landscape}
\begin{figure}[!ht]
\centering
\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
\vspace{0.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{figure}
\end{landscape}

@@

\begin{figure}[htb]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth, height=7.8cm]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

>>>>

---
title:  |
        | The Effect of Legislature Size on Public Spending:
        | A Meta-Analysis
date: \today
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we conduct the first meta-analysis that assesses the generality of the \"law of $1/n$\". Based on a sample of 30 articles, we find no robust evidence for the effect of legislature size on government budgets. Yet the aggregate results show significant heterogeneity. We find moderate support for the \"law of $1/n$\" in unicameral legislatures and in the upper house, but panel/fixed-effects models and regression discontinuity designs reduce public spending estimates. Electoral system does not strongly affect the \"law of $1/n$\", although one coefficient indicates that majoritarian systems may be more prone to overspending than others."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

export2md2<-function(x, which.table="descr", nmax=TRUE, header.labels=c(),
                    caption=NULL, format="html", width=Inf,
                    strip=FALSE, first.strip=FALSE, background="#D2D2D2",
                    size=NULL, landscape=FALSE,
                    header.background=NULL, header.color=NULL,
                    position="center", ...){

  trim <- function(x){
    x <- gsub("^[ ]+","",x)
    x <- gsub("[ ]+$","",x)
    x
  }

  prepare <- function (x, nmax, header.labels)
    {

        # x <- tab[1:3]
        # nmax <- TRUE
        # header.labels <- c()
        # names(attributes(x))

        show.all <- attr(x, "show.all")
        show.descr <- attr(x, "show.descr")
        groups <- attr(x, "groups")
        ny <- attr(x, "ny")
        all.last <- attr(x, "all.last")

        varnames <- attr(x, "varnames")
        nr <- attr(x, "nr")
        desc <- x$desc
        avail <- x$avail
        nmax.pos <- attr(x, "nmax.pos")
        nmax.avail.pos <- NULL
        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- integer(0)
        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) > 0) nmax.avail.pos <- nmax.pos[[2]] + 1
        if (length(nmax.pos[[1]]) > 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- 1
        if (length(nmax.pos[[1]]) > 0 & length(nmax.pos[[2]]) > 0) nmax.avail.pos <- c(1, nmax.pos[[2]])
        if (length(nmax.avail.pos) > 0 && nmax) {
            Nmax <- apply(avail[, nmax.avail.pos, drop = FALSE],2, function(x) max(as.double(x)))
        } else {
            Nmax <- NULL
            nmax <- FALSE
        }

        dd.pos <- attr(x, "dd.pos")
        j <- 1
        table1 <- NULL
        if (!is.null(attr(x, "caption")))
            cc <- character(0)
        for (i in 1:length(varnames)) {
            if (nr[i] == 1) {
                t.i <- desc[j, , drop = FALSE]
            } else {
                t.i <- rbind(rep(NA, ncol(desc)), desc[j:(j + nr[i] -
                                                              1), , drop = FALSE])
                rownames(t.i)[1] <- paste(varnames[i], ":", sep = "")
                rownames(t.i)[-1] <- sub(varnames[i], "", rownames(t.i)[-1], fixed = TRUE)
                rownames(t.i)[-1] <- sub(": ", "    ", rownames(t.i)[-1])
                if (length(dd.pos) < ncol(t.i)) {
                    t.i[1, -dd.pos] <- t.i[2, -dd.pos]
                    t.i[2, -dd.pos] <- NA
                }
            }
            table1 <- rbind(table1, t.i)
            j <- j + nr[i]
            if (!is.null(attr(x, "caption"))) {
                if (attr(x, "caption")[[i]] == "")
                    cc <- c(cc, rep("", NROW(t.i)))
                else cc <- c(cc, attr(x, "caption")[[i]], rep("",
                                                              NROW(t.i) - 1))
            }
        }
        if (ncol(table1) == 0) table1 <- table1[-1, ]
        if (nmax) table1 <- rbind(colnames(table1), c(paste("N=", Nmax, sep = ""), rep("", ncol(table1) - length(Nmax))), table1) else table1 <- rbind(colnames(table1), table1)
        table1 <- ifelse(is.na(table1), "", table1)
        if (length(header.labels)==6 && is.null(names(header.labels))){
            names(header.labels)<-c("all","p.overall","p.trend","ratio","p.ratio","N")
        }
        if ("all"%in%names(header.labels)){
            ww.all<-grep("^\\[ALL\\]",trim(table1[1,]))
            if (length(ww.all)>0){
                ww.all<-ww.all[1]
                table1[1,ww.all]<-header.labels["all"]
            }
        }
        if ("p.overall"%in%names(header.labels)){
            ww.p.overall<-which(table1[1,]=="p.overall")
            if (length(ww.p.overall)>0){
                ww.p.overall<-rev(ww.p.overall)[1]
                table1[1,ww.p.overall]<-header.labels["p.overall"]
            }
        }
        if ("p.trend"%in%names(header.labels)){
            ww.p.trend<-which(table1[1,]=="p.trend")
            if (length(ww.p.trend)>0){
                ww.p.trend<-rev(ww.p.trend)[1]
                table1[1,ww.p.trend]<-header.labels["p.trend"]
            }
        }
        if ("ratio"%in%names(header.labels)){
            ww.ratio<-which(table1[1,]%in%c("OR","HR"))
            if (length(ww.ratio)>0){
                ww.ratio<-rev(ww.ratio)[1]
                table1[1,ww.ratio]<-header.labels["ratio"]
            }
        }
        if ("p.ratio"%in%names(header.labels)){
            ww.p.ratio<-which(table1[1,]=="p.ratio")
            if (length(ww.p.ratio)>0){
                ww.p.ratio<-rev(ww.p.ratio)[1]
                table1[1,ww.p.ratio]<-header.labels["p.ratio"]
            }
        }
        if ("N"%in%names(header.labels)){
            ww.N<-which(table1[1,]=="N")
            if (length(ww.N)>0){
                ww.N<-rev(ww.N)[1]
                table1[1,ww.N]<-header.labels["N"]
            }
        }
        table1 <- apply(table1, 2, format, justify = "centre")
        colnames(table1) <- rep("", ncol(table1))

        table2 <- x[[2]]
        table2 <- as.matrix(table2)
        table2 <- ifelse(is.na(table2), "", table2)
        table2 <- rbind(colnames(table2), table2)
        table2 <- apply(table2, 2, format, justify = "centre")
        colnames(table2) <- rep("", ncol(table2))

        # rearrange table 1 and table 2 by putting all column after descriptives by groups.
        if (all.last & show.all & show.descr & groups){
            table1[,1:(ny+1)] <- table1[,c(2:(ny+1),1)]
        }
        if (all.last){
            table2[,1:(ny+1)] <- table2[,c(2:(ny+1),1)]
        }

        # out
        out <- list(table1 = table1, table2 = table2)
        if (!is.null(attr(x, "caption"))) attr(out, "cc") <- cc
        attr(out, "nmax") <- nmax
        nr <- ifelse(nr>1, nr+1, nr)
        nr <- cbind(nr, rep(0:1, length(nr))[1:length(nr)])
        nr <- unlist(apply(nr, 1, function(x) rep(x[2],x[1])))
        attr(out, "nr") <- nr
        out

    }

  # compiled.format <- try(rmarkdown::all_output_formats(knitr::current_input())[1],silent=TRUE)
  #
  # if (inherits(compiled.format, "try-error") || is.null(compiled.format)){
  #   warning("you are using export2md out of Rmarkdown context...")
  # } else {
  #   if (compiled.format%in%c("html_document","ioslides_presentation","slidy_presentation")) format <- "html"
  #   if (compiled.format%in%c("pdf_document","beamer_presentation")) format <- "latex"
  #   if (compiled.format=="word_document") format <- "markdown"
  # }

  if (missing(format)){
    format <- NA
    if (!interactive()){ # execute inside Rmarkdown
      if (knitr::is_html_output()) format="html"
      if (knitr::is_latex_output()) format="latex"
      if (!knitr::is_html_output() & !knitr::is_latex_output()) format="markdown"
      if (is.na(format)){
        warning("Unable to identify format -> HTML assigned.")
        format <- "html"
      }
    } else {# execute inside Rmarkdown
      warning("You are calling export2md outside Rmarkdown without specifying format -> html format is assigned")
      format <- "html"
    }
  }

  extras <- list(...)
  if (!inherits(x, "createTable"))
    stop("x must be of class 'createTable'")
  if (inherits(x, "cbind.createTable"))
    stop("x cannot be of class 'cbind.createTable'")
  ww <- charmatch(which.table, c("descr", "avail"))
  if (is.na(ww))
    stop(" argument 'which.table' must be either 'descr' or 'avail'")

  if (attr(x,"groups")){
    y.name.label<-attr(x,"yname")
  }

  if (!is.null(caption)){
    if (!is.character(caption))
      stop(" argument 'caption' must be a character'")
  } else {
    if (ww==1){
      if (attr(x,"groups"))
        if (inherits(x,"missingTable"))
          caption<-paste("Missingness table by groups of `",y.name.label,"'",sep="")
      else
        caption<-paste("Summary descriptives table by groups of `",y.name.label,"'",sep="")
      else
        if (inherits(x,"missingTable"))
          caption<-"Missingess table"
        else
          caption<-"Summary descriptives table"
    }
    if (ww==2){
      if (attr(x,"groups"))
        caption<-paste("Available data by groups of `",y.name.label,"'",sep="")
      else
        caption<-"Available data"
    }
  }
  pp <- compareGroups:::prepare(x, nmax = nmax, header.labels)
  #pp <- prepare(x, nmax = nmax, header.labels)
  cc <- unlist(attr(pp, "cc"))
  if (ww %in% c(1)) {
    table1 <- pp[[1]]
    ii <- ifelse(rownames(table1)[2] == "", 2, 1)
    table1 <- cbind(rownames(table1), table1)
    align <- c("l", rep("c", ncol(table1)))
    table1[1, 1] <- " "
    colnames(table1) <- table1[1, ]
    colnames(table1)[-1] <- trim(colnames(table1)[-1])
    table1 <- table1[-1, , drop = FALSE]
    table1[,2:ncol(table1)] <- apply(table1[,-1,drop=FALSE],2,trim)
    #table1 <- table1[-2]
    #names(table1)[1] <- 'Extended Sample'
    # N in the second row
    table1 <- table1[,-3]
    colnames(table1)[2] <- 'Extended Sample'
    n.exists <- nrow(table1) > 1 && length(grep("^N=", trim(table1[1, 2])))
    if (format=="latex" & strip)
      table1[((1+n.exists):nrow(table1)),ncol(table1)] <- ifelse(table1[((1+n.exists):nrow(table1)),ncol(table1)]=="", "\\vphantom{}", table1[((1+n.exists):nrow(table1)),ncol(table1)])
    if (format=="latex") caption <- gsub("%","\\\\%",caption)
    ans <- knitr::kable(table1, align = align, row.names = FALSE, caption=caption[1], format=format,
                        booktabs=format=="latex", longtable=TRUE, linesep="", ...)
    ans <- add_indent(ans, grep("^ ",table1[,1]))
    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
    # groups
    if (!is.null(cc)){
      for (cci in 1:length(cc)){
        if (cc[cci]!=""){
          group.label <- cc[cci]
          inici <- 0
          final <- 0
        } else {
          if (cc[cci-1]!="")
            group.begin <- cci-1
          if (cci==length(cc) || cc[cci+1]!=""){
            group.end <- cci
            ans <- group_rows(ans, group.label, group.begin+n.exists, group.end+n.exists)
          }
        }
      }
    }
    if (strip){
      nr <- attr(pp, "nr")
      ans <- row_spec(ans, which(nr==!first.strip)+n.exists, background = background)
    }
    if (n.exists){
      ans <- row_spec(ans, 1, hline_after=TRUE)
    }

    if (landscape) ans <- landscape(ans)
    if (format=="latex"){
      ans <- kable_styling(ans, latex_options = c("repeat_header"), font_size=size, position=position)
      #if (n.exists) ans <- gsub("\\\\midrule", "", ans) # remove lines after N
      if (n.exists) ans <- gsub("\\\\midrule\n\\\\endfirsthead", "\\\\endfirsthead", ans) # remove lines after N
      if (strip) ans <- gsub("\\textbackslash{}vphantom\\{\\}", "\\vphantom{}", ans, fixed=TRUE)
    }
    if (format=="html"){
      ans <- kable_styling(ans, bootstrap_options=c(if (!strip) "striped" else NULL, "condensed"), full_width=FALSE, font_size=size, position=position)
      ans <- row_spec(ans, 0, background=header.background, color=header.color)
      ans <- row_spec(ans, if (sum(unlist(attr(x, "nmax.pos")))>0) 1 else 0, italic=sum(unlist(attr(x, "nmax.pos")))>0, extra_css = "border-bottom: 1px solid grey")
    }
    return(ans)
  }
  if (ww %in% c(2)){
    # table2 <- compareGroups:::prepare(x, nmax = nmax, c())[[2]]
    table2 <- prepare(x, nmax = nmax, c())[[2]]
    table2 <- cbind(rownames(table2), table2)
    if (!is.null(attr(x, "caption"))) {
      cc <- unlist(attr(x, "caption"))
      table2[, 1] <- paste("    ", table2[, 1])
    }
    table2[1, 1] <- " "
    align <- c("l", rep("c", ncol(table2)))
    colnames(table2)[-1] <- trim(table2[1, -1])
    table2 <- table2[-1, ,drop=FALSE]
    ans <- knitr::kable(table2, align = align, row.names = FALSE, caption=caption[1], format=format, booktabs=format=="latex", longtable=TRUE, ...)
    # ans <- knitr::kable(table2, align = align, row.names = FALSE, caption=caption[1], format=format, booktabs=format=="latex")
    # groups
    if (!is.null(cc)){
      for (cci in 1:length(cc)){
        if (cc[cci]!=""){
          group.label <- cc[cci]
          inici <- 0
          final <- 0
        } else {
          if (cc[cci-1]!="")
            group.begin <- cci-1
          if (cci==length(cc) || cc[cci+1]!=""){
            group.end <- cci
            ans <- group_rows(ans, group.label, group.begin, group.end)
          }
        }
      }
    }
    ans <- add_indent(ans, integer())
    if (strip) ans <- row_spec(ans, which(rep(0:1, nrow(table2))[1:nrow(table2)]==!first.strip), background = background)
    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
    if (landscape) ans <- landscape(ans)
    if (format=="latex"){
      ans <- kable_styling(ans, latex_options = c("repeat_header"), font_size = size, position=position)
    }
    if (format=="html"){
      ans <- kable_styling(ans, bootstrap_options=c(if (!strip) "striped" else NULL, "condensed"), full_width = FALSE, font_size = size, position=position)
      ans <- row_spec(ans, 0, background=header.background, color=header.color)
      ans <- row_spec(ans, 0, italic=FALSE, extra_css = "border-bottom: 1px solid grey")
    }

    return(ans)
  }
}
```

@@

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We select `r length(unique(dat$id))` articles that
use quantitative methods to evaluate the impact of legislature size over
government spending across several dimensions. Our study sample mirrors the
diversity of the literature. We found studies that present both negative and positive coefficients, often reaching statistical significance in either. Given the volume and the disparity of
the studies, we employ meta-analysis to summarise the results. Meta-analysis
provides a rigorous approach to combine heterogeneous outcomes into a single
estimation, and it allows scholars to gain valuable insights from the
aggregated data [@cooper2019handbook; @hedges1985statistical]. Meta-analysis
can also identify potential sources of study variability, enabling researchers
to assess threats to external validity and direct future efforts into more
promising areas of academic inquiry [@doucouliagos2008democracy]. Research
synthesis methods have been successfully applied in medicine and psychology
since the 1970s [@glass2015meta], and our work contributes to the burgeoning
literature that uses meta-analytic methods to understand challenging questions
in political science [@costa2017responsive; @doucouliagos2008democracy;
@green2013field; @lau2007effects; @schwarz2020supporting].

We run meta-regressions to further evaluate the relationship
between legislature size and government expenditures. In those analyses, we
measure the effect of five moderators that capture different sources of
heterogeneity in the literature. In section G of the Supplementary Materials, we use binomial tests to assess whether the proportions of positive and negative coefficients in our
sample are statistically different from each other. We also construct a series of funnel plots to
test for publication bias in existing research on the "law of $1/n$"
[@easterbrook1991publication; @gerber2001testing].

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
aux$`Independent Variables` <- recode(aux$`Independent Variables`,
                                      `N` = "Lower Chamber Size",
                                      `K` = "Upper Chamber Size",
                                      `logN` = "Log of Lower Chamber Size")
aux$`Electoral system` <- recode(aux$`Electoral system`,
                                 `Non-Maj` = "Non-Majoritarian",
                                 `Maj` = "Majoritarian")
aux <- select(aux, usemeta2, `Independent Variables`, Year, `Published work`, `Estimation method`, `Institutional Design`, `Electoral system`)

aux3 <- descrTable(~.-usemeta2, 
                   aux, y = aux$usemeta2,
                   show.p.overall = F, 
                   show.all = T)
export2md2(aux3, 
           caption = "Descriptive Statistics of Moderators", 
           format  = "latex")
```
\normalsize

@@

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another building a common index for papers that share
the same data specifications. By adding these two levels, we account for
within- and between-study variation, thus removing these sources of effect size
dependency and improving the accuracy of the results. More information about
the multilevel models can be found in Section H.1 of the Supplementary
Material.

@@

The "law of $1/n$" states that more legislators increase government
expenditure. In this paper, we employ two methods to test the empirical
validity of that relationship.\footnote{We also run preliminary binomial Z
tests in section G of the Supplementary Materials.} First, we fit nine
multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
`dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
Then, we run four sets of meta-regressions to measure the effects of a group of
moderators on the effect sizes of our study sample. To recapitulate, our
independent variables of interest are lower chamber size, the natural logarithm
of lower chamber size, and upper chamber size. The dependent variables are
public expenditure per capita, the natural logarithm of public expenditure per
capita, and government expenditure as a percentage of GDP. Since the outcomes
have different scales, we treat them separately in our models.

@@

@@

We begin with the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the nine variable combinations, we found only seven the article
pool. Our sample does not contain any papers that analyse the relationships
between log lower chamber size and public expenditure per capita, or between
upper chamber size and the logarithm of public expenditure per capita.

@@

\begin{landscape}
\begin{figure}[!ht]
\centering
\caption{Forest plots of the relationship between legislature size and government spending (main sample)}
\vspace{0.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{figure}
\end{landscape}

@@

\begin{figure}[htb]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (main sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth, height=7.8cm]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}
